A preliminary constraint grammar for Russian

### 2015-05-04 2015-nodalida-ruscg/ruscg.tex
added sharoff reference
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60234 72bbbca6-d526-0410-a7d9-f06f51895060

Note that the final accuracy is below the state of the art for Russian, however the state of
the art employs unavailable training corpora of over five million tokens.\rr{citations? This comes out of the blue.}

\begin{figure*}
  \centering
  \includegraphics[width=0.70\textwidth]{graphics/learning-curve.pdf}
  \caption{Learning curve for three taggers, \texttt{hunpos} with no lexicon, 
    \texttt{hunpos} with a lexicon, and \texttt{hunpos} with a lexicon and the 
    Russian constraint grammar in a voting set up.}
  \label{fig:curve}
\end{figure*}
\rr{R2: If I interpret Fig. 3 correctly, the HMM system alone is much more dependent on training corpus size than the voting set-up, where accuracies actually appear to become asymptotic already with 8-10,000 words in the training corpus, indicating that further improvement depends more on the CG than the HMM-component.}
\section{Future work}
\label{sec:future}
% ROB
% FRAN
% func analysis
% dep analysis

@@

We have a number of plans for future work, the first is increasing the precision of the grammar without
decreasing recall. Secondly we would like to add syntactic function labelling and dependency parsing. For 
the dependency parse we plan to reuse the Giellatekno dependency grammar as in \cite{antonsen10}.

>>>>

The final accuracy is below the state of the art for Russian. For instance, 
\newcite{sharoff08lrec-mocky} report a maximum accuracy of 95.28\% using the TnT tagger.
Note, however, that this model was trained on a much larger corpus -- over five million
tokens -- which is not freely available.

\begin{figure*}
  \centering
  \includegraphics[width=0.70\textwidth]{graphics/learning-curve.pdf}
  \caption{Learning curve for three taggers, \texttt{hunpos} with no lexicon, 
    \texttt{hunpos} with a lexicon, and \texttt{hunpos} with a lexicon and the 
    Russian constraint grammar in a voting set up.}
  \label{fig:curve}
\end{figure*}
\rr{R2: If I interpret Fig. 3 correctly, the HMM system alone is much more dependent on training corpus size than the voting set-up, where accuracies actually appear to become asymptotic already with 8-10,000 words in the training corpus, indicating that further improvement depends more on the CG than the HMM-component.}

\section{Future work}
\label{sec:future}
% ROB
% FRAN
% func analysis
% dep analysis

@@

We have a number of plans for future work, the first of which is increasing the precision of the grammar without
decreasing recall. Secondly we would like to add syntactic function labelling and dependency parsing. For 
the dependency parse we plan to reuse the Giellatekno dependency grammar as in \cite{antonsen10}.
